### 2009-11-26 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
outline version.

It is further recognized that most sensor observations consist of at least two processes: a sampling process and a conversion process.
The 
 \begin{figure}
\includegraphics{SensorML_SenseTile_System_design_tuple_pa3.png}
\caption{Block diagram of SenseTile System process}\label{fig:SensorML_SenseTile_design.png}
\end{figure}

@@

public class DataBlockInt extends AbstractDataBlock

\newpage
\section{BON to SensorML mapping}

\chapter{Design}
High level design
\section{SenseTile Web Service}
 \begin{figure}
\scalebox{0.65}{\includegraphics{sensetile_static_diagam.png}}
\caption{SenseTile Static Diagram}\label{fig:sensetile_static_diagam.png}
\end{figure}
DataProducer - use PacketInput stream to access SenseTile observation packets.

Steps in the process these sensorml components are roughly.

System reads packets and averages them for every configurable seconds. Defalut 1.

@@

DataProvider - provides an RMI interface to the DataProducer to update. Provides a Web Service interface  based on Sensor Observation Service. Not fully as is a very complex interface.

\newpage
\section{SensorML generation tool}

BON to SensorML mapping.

Features to be elements or attributes.

@@

@@

RMI used between DataProvider and DataProducer.
\chapter{Results}

@@

>>>>

It is further recognized that most sensor observations consist of at least two processes: a sampling process and a conversion process.

 \begin{figure}
\includegraphics{SensorML_SenseTile_System_design_tuple_pa3.png}
\caption{Block diagram of SenseTile System process}\label{fig:SensorML_SenseTile_design.png}
\end{figure}

@@

\newpage
\section{BON to SensorML mapping}
Features to be elements or attributes.

SML prefix to handled key word clashes between sensorML and BON.

How to display this in thesis?
\chapter{Design}

\section{SenseTile Web Service}
\subsection{Overview}
 \begin{figure}
\scalebox{0.65}{\includegraphics{SystemOverview.png}}
\caption{SenseTile System Overview}\label{fig:SystemOverview.png}
\end{figure}

 \begin{figure}
\scalebox{0.65}{\includegraphics{sensetile_static_diagam.png}}
\caption{DataProducer Static Diagram}\label{fig:sensetile_static_diagam.png}
\end{figure}

\subsection{DataProducer}
Use PacketInput stream to access SenseTile observation packets.

System reads packets and averages them for every configurable seconds. Default 1.

@@

Observation as described in SOS.

\subsection {DataProvider}

Keeps track of sensorboards that register

provides an RMI interface to the DataProducer to update with observations.

GetObservaton - marshal Observation to xml string and send as response.

StreamObservation -  registered clients get new observation sent over UDP connection?

Provides a Web Service interface  based on Sensor Observation Service. Not fully as is a very complex interface.

\newpage
\section{SensorML generation}

@@

 component id +Input

 component id+Output

@@

RMI used between DataProvider and DataProducer.

\section{SensorML Generation}

\chapter{Results}

@@

Generation of SensorML description of a Senstile Sensor
